timesliced_random_cell_selection

### 2019-01-08 src/timesliced_random_cell_selection.Rmd
??

Second you need to put the background (background_all) into a spatialpointsdataframe.
```{r}
background_all2 <- background_all[background_all$year == 2007, ]
xy <- background_all2[ ,c("longitude_meters","latitude_meters")] # This is to tell R where the coordinates are. Note that the column order needs to be longitude, latitude

@@

    }
}
write.csv(background_all_sp, "../output/bio/background_complete_2007.csv", row.names = FALSE)
background_all2 <- as.data.frame(background_all_sp)
head(background_all_sp)
```

>>>>

Second you need to put the background (background_all) into a spatialpointsdataframe.
```{r}
background_all2 <- background_all[background_all$year == 2009, ]
xy <- background_all2[ ,c("longitude_meters","latitude_meters")] # This is to tell R where the coordinates are. Note that the column order needs to be longitude, latitude

@@

    }
}
write.csv(background_all_sp, "../output/bio/background_complete_2009.csv", row.names = FALSE)
background_all2 <- as.data.frame(background_all_sp)
head(background_all_sp)
```
